---
author: Tingwei Adeck
date: '`r format(Sys.time(), "%B %d, %Y")`'
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tidyDenovix

[![Project status](https://www.repostatus.org/badges/latest/concept.svg)](https://github.com/AlphaPrime7/tidyDenovix/graphs/commit-activity) [![Project Status](https://www.repostatus.org/badges/latest/wip.svg)](https://github.com/AlphaPrime7/tidyDenovix/graphs/commit-activity)
[![Maintenance](https://img.shields.io/badge/Maintained%3F-yes-green.svg)](https://github.com/AlphaPrime7/tidyDenovix/graphs/commit-activity)

The goal of [`{tidyDenovix}`](https://github.com/AlphaPrime7/tidyDenovix) is to clean data obtained from the Denovix spectrophotometry instrument. This package should clean data for RNA or DNA samples. At the moment users should use the 'lax' option for quality control.

## Installation

You can install the development version of tidyDenovix from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("AlphaPrime7/tidyDenovix")
```

## Raison-Etre

- Upon using the Denovix, the user can take screenshots of the screen if they intend to present this data at a conference or seminar. However, the screenshots taken are not very professional and will likely not look good at a conference.
- As an undergraduate student I was faced with this issue and with poor programming skills, I had a hodgepodge of code lines that created an image but was not reproducible even by me because I had no idea what I was doing.
- Fast forward today and this package will accomplish cleaning this type of data making it ready for plotting and presenting to faculty and peers.

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(tidyDenovix)
## basic example code
fpath <- system.file("extdata", "rnaspec2018.csv", package = "tidyDenovix", mustWork = TRUE)
rna_data = tidyDenovix(fpath, file_type = 'csv', sample_type = 'RNA', check_level = 'lax')
```


## Quality Control

- As always quality is important so there are some quality parameters. Play around with the check_level parameter as 'lax' vs 'strict' to determine the level of quality needed for the final output.

- The 'strict' option right now does not retain sample names but that will be worked on before the initial final release. If not that will be worked on later.

## References

- Coming soon!!!

